---
title: "01_R-spatial"
author: "Steve, Yu"
date: "2020/5/25"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls()); invisible(gc())
library(knitr)
library(dplyr)
library(sf)
library(sp)
library(rgdal)
library(raster)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(ggplot2)
library(ggmap)
library(tmap)
library(leaflet)
opts_chunk$set(echo = TRUE)
```

# Chapter 1

## section 1.1

page 07

### section 1.1.1

page 08

page 09

```{r}
ln1 <- matrix(runif(6), ncol=2) %>% Line()
str(ln1); ln1
```

```{r}
ln2 <- Line(matrix(runif(6), ncol=2))
```

```{r}
lns1 <- Lines(list(ln1), ID = c("hwy1"))
lns2 <- Lines(list(ln2), ID = c("hwy2"))

# ---
# lns1: just a geometric objects
lns1 %>% class()
lns1 %>% str()
```

```{r}
sp_lns <- SpatialLines(list(lns1, lns2))
sp_lns %>% str()

# ---
# plot successfully only if it is Spatial* class
# plot(sp_lns)

# ---
sp_lns@bbox # min and max in both x and y
ln1@coords[,1] %>% range
ln1@coords[,2] %>% range
ln2@coords[,1] %>% range
ln2@coords[,2] %>% range
```

page 10

```{r}
dfr <- data.frame(id = c("hwy1", "hwy2"), # note how we use the same IDs from above!
cars_per_hour = c(78, 22))
sp_lns_dfr <- SpatialLinesDataFrame(sp_lns, dfr, match.ID = "id")
sp_lns_dfr %>% str()
```

### section 1.1.2

page 10

page 11

page 12

```{r}
lnstr_sfg1 <- st_linestring(matrix(runif(6), ncol = 2))
lnstr_sfg2 <- st_linestring(matrix(runif(6), ncol = 2))

# ---
# see the class, structure and plot
lnstr_sfg1 %>% class()
lnstr_sfg1 %>% str
lnstr_sfg1 %>% plot
lnstr_sfg1
```

```{r}
lnstr_sfc <- st_sfc(lnstr_sfg1, lnstr_sfg2) # just one feature here

# ---
# see the class, structure and plot
lnstr_sfc %>% class
lnstr_sfc %>% str
lnstr_sfc %>% plot
lnstr_sfc
```

```{r}
lnstr_sf <- st_sf(dfr , lnstr_sfc)

# ---
# see the class, structure and plot
lnstr_sf %>% class
lnstr_sf %>% str
lnstr_sf %>% plot
lnstr_sf
```

page 13

```{r}
methods(class="sf")
```

```{r}
library(data.table)
# Challenge
# [R Spatial Cheatsheet](https://www.maths.lancs.ac.uk/~rowlings/Teaching/UseR2012/cheatsheet.html)
```

```{r}
# ---
# sp
# points from scratch
tmp_df <- data.table(t1 = LETTERS[1:5])
set.seed(9527)
pt_coords <- runif(10) %>% matrix(., ncol = 2)
pt_sp = SpatialPoints(pt_coords)

# make spatial data frame
spdf = SpatialPointsDataFrame(pt_coords, tmp_df)
spdf = SpatialPointsDataFrame(pt_sp, tmp_df)

# promote data frame to spatial
x <- runif(5); y <- runif(5)
coordinates(tmp_df) = cbind(x, y)

# back to data
tmp_df %>% data.frame() #cannot use data.table()
tmp_df$t1
tmp_df %>% bbox
tmp_df %>% str

# manipulate data.frame
tmp_df[tmp_df$t1 %in% c("B", "D", "E"), ]
```

```{r}
# ---
# sf
tmp_df <- data.table(t1 = LETTERS[1:2])
set.seed(9527)
pt1_coords <- runif(10) %>% matrix(., ncol = 2)
pt2_coords <- runif(10) %>% matrix(., ncol = 2)

# points from scratch
st_point(x = c(1,2))
st_multipoint(x = pt1_coords)
st_multipoint(x = pt1_coords, dim = "XY")
ptstr_sfg1 <- st_multipoint(x = pt1_coords)
ptstr_sfg2 <- st_multipoint(x = pt2_coords)
ptstr_sfg1 %>% class
# ptstr_sfg1 %>% str

# combine all single feature objects
ptstr_sfc <- st_sfc(ptstr_sfg1, ptstr_sfg2)
# ptstr_sfc %>% class
# ptstr_sfc %>% str

# add atribute
ptstr_sf <- st_sf(tmp_df, ptstr_sfc)
ptstr_sf %>% class
# ptstr_sf %>% str
# ptstr_sf

# manipulate data.fram
# 可以用 dplyr
# ptstr_sf[ptstr_sf$t1=="A", ]
ptstr_sf %>% filter(t1=="A")
st_bbox(ptstr_sf)
```

## section 1.2

## section 1.2.1

page 14

```{r}
philly_homicides_df <- read.csv("../data/philly_homicides.csv")

# ---
philly_homicides_df %>% class()
philly_homicides_df %>% str()
```

```{r}
philly_homicides_sf <- st_as_sf(philly_homicides_df, coords = c("POINT_X", "POINT_Y"))

# ---
philly_homicides_sf %>% class()
philly_homicides_sf %>% str()
philly_homicides_sf$geometry
```

page 15

```{r}
st_crs(philly_homicides_sf)
```

```{r}
st_crs(philly_homicides_sf) <- 4326 # we can use EPSG as numeric here
st_crs(philly_homicides_sf)
```

```{r}
# st_write(philly_homicides_sf, "../data/PhillyHomicides", driver = "ESRI Shapefile")

# ---
# to force the save:
st_write(obj = philly_homicides_sf, 
         dsn = "../data/PhillyHomicides", 
         driver = "ESRI Shapefile", 
         delete_layer = TRUE)
```

### section 1.2.2

page 15

```{r}
philly_homicides_df %>% class()

# ---
# original class is dataframe
# after setting coordinate, its class become sp
coordinates(philly_homicides_df) <- c("POINT_X", "POINT_Y")
philly_homicides_df %>% class()
```

page 16

```{r}
is.projected(philly_homicides_df) # see if a projection is defined
```

```{r}
proj4string(philly_homicides_df) <- CRS("+init=epsg:4326") # this is WGS84
is.projected(philly_homicides_df) # voila! hm. wait a minute..
```

```{r}
# actually, projection is set successfully.
philly_homicides_df %>% str
```

```{r}
# to save out using writeOGR from rgdal
library(rgdal)

# note that we need to save the philly_homicides_df, which we converted to sp object!
# writeOGR(obj = philly_homicides_df, 
#          dsn = "../data/PhillyHomicides", 
#          layer = "PhillyHomicides", driver = "ESRI Shapefile")

# to force save:
writeOGR(obj = philly_homicides_df, 
         dsn = "../data/PhillyHomicides", 
         layer = "PhillyHomicides", 
         driver = "ESRI Shapefile", 
         overwrite_layer = TRUE)
```

## section 1.3

### section 1.3.1

page 16

```{r}
# read in
philly_sf <- st_read("../data/Philly")
```

```{r}
philly_sf %>% str
```

page 17

```{r}
plot(philly_sf)
```

```{r}
philly_sf %>% st_geometry() %>% plot
```

page 18

```{r}
# subset the familar way
philly_sf_rich <- philly_sf[philly_sf$medHHinc > 60000, ]
# or
philly_sf_rich <- subset(philly_sf, medHHinc > 60000)

# ---
# run the folloeing codes at same time
philly_sf %>% st_geometry() %>% plot
plot(st_geometry(philly_sf_rich), add = T, col = "red")
```

```{r}
philly_sf %>% st_geometry() %>% plot
philly_sf %>%
  filter(medHHinc > 60000) %>%
  st_geometry() %>%
  plot(col = "red", add = T)
```

### section 1.3.2

page 19

```{r}
library(rgdal)
philly_sp <- readOGR(dsn = "../data/Philly", layer = "PhillyTotalPopHHinc")
```

```{r}
class(philly_sp)
```

```{r}
plot(philly_sp)
philly_sp_rich <- subset(philly_sp, medHHinc > 60000)
plot(philly_sp_rich, add = T, col = "red")
```

## section 1.4

page 20

```{r}
library(raster)
# specify the RasterLayer with the following parameters:
# - minimum x coordinate (left border)
# - minimum y coordinate (bottom border)
# - maximum x coordinate (right border)
# - maximum y coordinate (top border)
# - resolution (cell size) in each dimension
r <- raster(xmn=-0.5, ymn=-0.5, xmx=4.5, ymx=4.5, resolution = c(1,1))
r
```

```{r}
class(r)
```

```{r}
r <- setValues(x = r, values = runif(25))
class(r)
r
r$layer@data
```

page 21

```{r}
coordinates(r) #coordinate會是grid的中心~
plot(r); points(coordinates(r), pch = 3)
```

```{r}
class(volcano)
volcano %>% dim
```

```{r}
volcano.r <- raster(x = volcano)
class(volcano.r)

# ---
# plot
plot(volcano.r)
```

```{r}
library(raster)
HARV <- raster("../data/HARV_RGB_Ortho.tif")
```

```{r}
# 注意 band: 1  (of  3  bands)
HARV
```

page 22

```{r}
plot(HARV)
```

page 22

```{r}
crs(HARV)
```

```{r}
methods(class = class(HARV))
```

page 23

```{r}
hist(HARV)
```

```{r}
ncell(HARV)
```

```{r}
hist(HARV, maxpixels = ncell(HARV))
```

page 24

```{r}
# explore raster metadata before loading them
GDALinfo("../data/HARV_RGB_Ortho.tif")
```

```{r}
nlayers(HARV) # 1，因為指讀取一個band
nbands(HARV) # 應該是用這個看有多少個 band 才對。
```

```{r}
HARV_Band2 <- raster("../data/HARV_RGB_Ortho.tif", band = 2)
plot(HARV_Band2)
```

page 25

```{r}
HARV_stack <- stack("../data/HARV_RGB_Ortho.tif")
```

```{r}
# how many layers?
nlayers(HARV_stack) #3

# nbands(HARV_stack) #會是error。not implemented for RasterStack objects
```

```{r}
HARV_stack
```

```{r}
plot(HARV_stack)
```

```{r}
plotRGB(HARV_stack)
```

### section 1.4.1

page 27

```{r}
object.size(HARV_stack)
```

```{r}
HARV_brick <- brick(HARV_stack)
object.size(HARV_brick)
```

page 28

```{r}
# specify the grid topology with the following parameters:
# - the smallest coordinates for each dimension, here: 0,0
# - cell size in each dimension, here: 1,1
# - number of cells in each dimension, here: 5,5
gtopo <- GridTopology(cellcentre.offset = c(0,0), 
                      cellsize = c(1,1), 
                      cells.dim = c(5,5)) # create the grid
datafr <- data.frame(runif(25)) # make up some data
SpGdf <- SpatialGridDataFrame(grid = gtopo, data = datafr) # create the grid data frame
summary(SpGdf)
```

```{r}
coordinates(SpGdf) #coordinate會是grid的中心~
plot(SpGdf); points(coordinates(SpGdf), pch = 3)
```

# chapter 2

## section 2.1

page 29

```{r}
ph_edu <- read.csv("../data/PhillyEducation.csv")
names(ph_edu)
```

### section 2.1.1

```{r}
## sf ##
# if you need to read in again:
philly_sf <- st_read("../data/Philly")
names(philly_sf)
```

page 30

```{r}
philly_sf_merged <- merge(x = philly_sf, y = ph_edu, 
                          by.x = "GEOID10", by.y = "GEOID")
names(philly_sf_merged)
```

### section 2.1.2

```{r}
## sp ##
# if you need to read in again:
philly_sp <- readOGR(dsn = "../data/Philly", layer = "PhillyTotalPopHHinc")

# this is sp::merge()
philly_sp_merged <- sp::merge(philly_sp, ph_edu, by.x = "GEOID10", by.y = "GEOID")
names(philly_sp_merged) # no geometry column here
```

## section 2.2

page 30

```{r}
## How about:

# 1. Get the census tract polygons.
# 2. Find the Philadelphia city center coordinates.
# 3. Create a buffer around the city center point.
# 4. Select all census tract polygons that intersect with the center buffer
```

### section 2.2.1

page 31

```{r}
# if you need to read in again:
philly_sf <- st_read(dsn = "../data/Philly", quiet = T)
# philly_sf %>% class
# philly_sf %>% str

# ---
# make a simple feature point with CRS
philly_ctr_sfc <- st_point(c(1750160, 467499.9)) %>% st_sfc(., crs = 102003)
# philly_ctr_sfc %>% class
# philly_ctr_sfc %>% str
philly_ctr_sfc

# ---
# plot(philly_ctr_sfc)
```

```{r}
# st_crs(philly_ctr_sfc)$units # unit is meter
philly_buf_sf <- st_buffer(philly_ctr_sfc, dist = 2000) # unit is meter
philly_buf_sf

# ---
# plot(philly_buf_sf)
```

```{r}
# ---
# check projection
philly_buf_sf %>% st_crs()
philly_sf %>% st_crs()
st_crs(philly_buf_sf) == st_crs(philly_sf)

# ---
philly_buf_intersects <- st_intersects(x = philly_buf_sf, y = philly_sf)
```

```{r}
# if above code fail, check those spatial objects coordinates
st_crs(philly_sf)
st_crs(philly_buf_sf)
```

page 32

```{r}
st_crs(philly_sf) <- 102003

# ---
st_crs(philly_sf)
st_crs(philly_buf_sf)
```

```{r}
philly_buf_intersects <- st_intersects(philly_buf_sf, philly_sf)
philly_buf_intersects %>% class()
```

```{r}
philly_buf_intersects
philly_buf_intersects[[1]]
```

```{r}
philly_sel_sf <- philly_sf[philly_buf_intersects[[1]], ]

# plot
plot(st_geometry(philly_sf), 
     border = "#aaaaaa", #灰色
     main = "Census tracts that fall within 2km of city center")
plot(st_geometry(philly_sel_sf), add = T, col = "red")
plot(st_geometry(philly_buf_sf), add = T, lwd = 2, lty = 2,
     col = scales::alpha("green", 0.5))

# ---
# if sf - data.frame object has lots of attributes, 
# you can use st_geometry() to extract polygon boundary only.
# plot(st_geometry(philly_sf), 
#      border = "#aaaaaa", #灰色
#      main = "Census tracts that fall within 2km of city center")
# plot(st_geometry(philly_sel_sf), add = T, col = "red")
# plot(philly_buf_sf, add = T, lwd = 2, lty = 2, col = scales::alpha("green", 0.5))
```

### section 2.2.2

page 32  
page 33

```{r}
library(rgeos)
# if you need to read it in again
# verbose: report progress
philly_sp <- readOGR(dsn = "../data/Philly", 
                     layer = "PhillyTotalPopHHinc", 
                     verbose = T)
```

```{r}
coords <- data.frame(x = 1750160, y = 467499.9) # set the coordinates
prj <- CRS("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs") # the projection string for AEA
philly_ctr_sp <- SpatialPoints(coords, proj4string = prj) # create the spatialPoints
# philly_ctr_sp %>% str
# philly_ctr_sp %>% plot()
```

```{r}
# prj #敘述中有描述單位。+unit=m
philly_buf_sp <- gBuffer(spgeom = philly_ctr_sp, width=2000) # create buffer around center
# 單位為meter

# ---
# philly_buf_sp %>% plot()
# philly_buf_sp %>% str
```

```{r}
philly_buf_intersects <-  gIntersects(spgeom1 = philly_buf_sp, 
                                      spgeom2 = philly_sp, 
                                      byid=TRUE) 

# what kind of object is this?
class(philly_buf_intersects)# matrix, TRUE or FALSE
# philly_buf_intersects %>% dim #384 1

# subset
philly_sel_sp <- philly_sp[as.vector(philly_buf_intersects),]

# plot
plot (philly_sp, border = "#aaaaaa")
plot (philly_sel_sp, add = T, col = "red") 
plot (philly_buf_sp, add = T, lwd = 2, col = scales::alpha("green", 0.5))
```

## section 2.3

page 33  
page 34

```{r}
#If you need to read the file back in:
philly_homicides_sf <- st_read(dsn = "../data/PhillyHomicides")
st_crs(philly_homicides_sf)
st_crs(philly_sf)
```

```{r}
st_crs(philly_sf)
philly_homicides_sf_aea <- st_transform(x = philly_homicides_sf, 
                                        crs = st_crs(philly_sf))
```

```{r}
st_crs(philly_homicides_sf_aea)
st_crs(philly_sf)
```

```{r}
st_coordinates(philly_homicides_sf) %>% range()
st_coordinates(philly_homicides_sf_aea) %>% range()
```

```{r}
par(mfrow=c(1,2))
plot(st_geometry(philly_homicides_sf), axes=TRUE, main = "before transform - latlon")
plot(st_geometry(philly_homicides_sf_aea), axes=TRUE, main = "after transform - aea")
```

page 35

```{r}
st_write(obj = philly_homicides_sf_aea, 
         dsn = "../data/PhillyHomicides_aea", 
         driver = "ESRI Shapefile", 
         delete_layer = T)
```

### section 2.3.1

```{r}
philly_homicides_sp <- readOGR(dsn = "../data/PhillyHomicides", 
                               layer = "PhillyHomicides")
```

```{r}
proj4string(philly_sp)
proj4string(philly_homicides_sp)
```

```{r}
philly_homicides_sp_aea <- spTransform(philly_homicides_sp, CRS(proj4string(philly_sp)))
```

```{r}
## check the coordinates ##
range(coordinates(philly_homicides_sp_aea))
range(coordinates(philly_homicides_sp))
```

```{r}
## write out
writeOGR(obj = philly_homicides_sp_aea, 
         dsn = "../data/PhillyHomicides_aea",
         layer = "PhillyHomicides_aea", 
         driver = "ESRI Shapefile", 
         overwrite_layer = T)
```

### section 2.3.2

page 35

```{r}
# if you need to load again:
HARV <- raster("../data/HARV_RGB_Ortho.tif")
crs(HARV)
```

page 36

```{r}
HARV_WGS84 <- projectRaster(HARV, crs = "+init=epsg:4326")
```

```{r}
extent(HARV)
extent(HARV_WGS84)
```

```{r}
ncell(HARV)
ncell(HARV_WGS84)
```

```{r}
plot(HARV, main = "before transform - UTM")
```

```{r}
plot(HARV_WGS84, main = "after transform - WGS84")
```

## section 2.4

### section 2.4.1

page 37

```{r}
# ---
# Geometry polygon
# philly_sf <- st_read(dsn = "../data/Philly", quiet = T)

# ---
# Homicide data and latlon(Geometry point)
# philly_homicides_sf <- st_read(dsn = "../data/PhillyHomicides")
# philly_homicides_sf_aea <- st_transform(x = philly_homicides_sf,
#                                         crs = st_crs(philly_sf))

```

```{r}
# actually, philly_sf has attribute - Shape_area
# it almost equal to tract_area. 
# unit: sqare meter

# ---
# philly_sf %>% head()
# philly_sf %>% dim() #384 18

# ---
# st_crs(philly_sf) #unit=m
philly_sf %>% 
  mutate(tract_area = st_area(geometry)) %>% 
  head()
```

```{r}
philly_homicides_sf_aea %>% head
# philly_homicides_sf_aea %>% dim # 3883 9
```

```{r}
# dimension: 3886 27(9+18-1+1)
philly_sf %>% 
  mutate(tract_area = st_area(geometry)) %>% 
  st_join(x = ., y = philly_homicides_sf_aea) %>% 
  head()
```

page 38

```{r}
# 原始版本的 unique 會出錯，因為 tract_area 計算出來的面積大小可能有誤差。
# 雖然結果顯示 homic_rate 為[1/m^2]，但實際上我們已經轉換為[1/km^2]
crime_rate <- philly_sf %>% 
  mutate(tract_area = st_area(geometry)) %>%
  st_join(philly_homicides_sf_aea) %>%
  group_by(GEOID10) %>% 
  summarize(n_homic = n(),
            tract_area = tract_area[1],
            homic_rate = n_homic/tract_area * 1e6) 
```

```{r}
plot(crime_rate)
plot(crime_rate[, "homic_rate"], main = "homic_rate[1/km^2]")
```

```{r}
# 會爆出一堆eror
# 這些error在GDAL驅動程序中，因此無法通過sf進行更改
# 主要是數值轉換上的問題，主因是數值的位數太大了
# - [st_write: values not successfully written · Issue #69 · HeritageNetwork/Regional_SDM](https://github.com/HeritageNetwork/Regional_SDM/issues/69)
# - [Misleading warning · Issue #306 · r-spatial/sf](https://github.com/r-spatial/sf/issues/306)
# - [#6803 (ogr2ogr complains possibly due to too larger number) – GDAL](https://trac.osgeo.org/gdal/ticket/6803)

# ---
# 總之，這個錯誤無法解決，除非改變數值大小
# 或許之後逐漸淘汰 shpafile 的作法(?)
# 換成新的資料交換格式是 Geojson，不知道會不會比較好用XD

# ---
# as.character() also fail, because it still store as numeric when saving
# divided by 1e4, transfer to float, seems can slove the problem.
crime_rate$GEOID10 <- crime_rate$GEOID10 / 10000
st_write(obj = crime_rate,
         dsn = "../data/PhillyCrimerate", 
         layer = "PhillyCrimerate_sf", 
         driver = "ESRI Shapefile", update = T, delete_layer = T)
```

### section 2.4.2

page 39

```{r}
# just count length, so take any attribute is fine.
philly_homicides_sp_aea %>% names

# ---
ph_hom_count_sp <- aggregate(x = philly_homicides_sp_aea["OBJ_ID"], 
                             by = philly_sp, FUN = length)

# make sure we understand this error message:
# it's not error. it just calculate more attribute than we need.
# aggregate(x = philly_homicides_sp_aea, by = philly_sp, FUN = length)
```

```{r}
class(ph_hom_count_sp)
names(ph_hom_count_sp)
head(ph_hom_count_sp)
```

```{r}
library(rgeos)
gArea(ph_hom_count_sp, byid = T) %>% head()

# we multiply by by 1000000 to get sq km.
ph_hom_count_sp$homic_dens <- 1e6 * (ph_hom_count_sp$OBJ_ID/gArea(ph_hom_count_sp, 
                                                                  byid = TRUE))

hist(ph_hom_count_sp$homic_dens)
```

```{r}
plot(ph_hom_count_sp)
plot(ph_hom_count_sp[which(ph_hom_count_sp$homic_dens>20),], col = "red", add = T)
```

```{r}
ph_hom_count_sp %>% head
writeOGR(obj = ph_hom_count_sp, 
         dsn = "../data/PhillyCrimerate", 
         layer = "PhillyCrimerate_sp", 
         driver = "ESRI Shapefile", overwrite_layer = T)
```

# chapter 3

## section 3.1

page 41

```{r}
philly_crimes_sf <-  st_read(dsn = "../data/PhillyCrimerate", 
                             layer = "PhillyCrimerate_sf",
                             quiet = TRUE)
plot(philly_crimes_sf)
```

page 42

```{r}
# because this is a numeric vector!
plot(philly_crimes_sf$homic_rate)
```

page 43

```{r}
philly_crimes_sf[, "homic_rate"] %>% plot()
philly_crimes_sf$homic_rate %>% hist()
```

page 44

```{r}
plot(philly_crimes_sf[, "homic_rate"], 
     main = "Philadelphia homicide density per square km", 
     breaks = "quantile")
```

```{r}
library(RColorBrewer)
pal <- brewer.pal(7, "OrRd") # we select 7 colors from the palette
class(pal)
```

```{r}
plot(philly_crimes_sf["homic_rate"], 
     main = "Philadelphia homicide density per square km", 
     breaks = "quantile", nbreaks = 7,
     pal = pal)
```

## section 3.2

page 45

```{r}
philly_crimes_sp <- readOGR(dsn = "../data/PhillyCrimerate", 
                            layer = "PhillyCrimerate_sf", 
                            verbose = FALSE) 
names(philly_crimes_sp)
```

```{r}
# speed of spplot is a little bit slow,
# and it will put values of all attribute in same scale.

# ---
# spplot(philly_crimes_sp) 
spplot(philly_crimes_sp, "homic_rate")
spplot(philly_crimes_sp, c("n_homic", "homic_rate")) #會放到同一尺度，可能要學習進階設定
```

page 46

```{r}
library(classInt)

# quantile breaks
breaks_qt <- classIntervals(philly_crimes_sp$homic_rate, n = 7, style = "quantile")
br <- breaks_qt$brks 

# in order to cover lower and upper boundary, 
# need to expand a little bit for the lowest and largest.
offs <- 0.0000001 
br[1] <- br[1] - offs 
br[length(br)] <- br[length(br)] + offs 

# categoreis for choropleth map
philly_crimes_sp$homic_rate_bracket <- cut(philly_crimes_sp$homic_rate, br)

# plot
spplot(philly_crimes_sp, "homic_rate_bracket", 
       col.regions = pal, 
       main = "Philadelphia homicide density per square km")
```

## section 3.3

page 47

```{r}
# library(ggplot2)
# ggplot(data = my_data_frame, 
#        mapping = aes(x = name_of_column_with_x_value, 
#                      y = name_of_column_with_y_value)) +
#   geom_point()

# ---
# ggplot(my_data_frame, 
#        aes(name_of_column_with_x_value, 
#            name_of_column_with_y_value)) +
#   geom_point()
```

page 48

```{r}
ggplot(philly_crimes_sf) + 
  geom_sf(aes(fill=homic_rate))
```

```{r}
library(classInt)

# get quantile breaks. Add .00001 offset to catch the lowest value
breaks_qt <- classIntervals(var = c(min(philly_crimes_sf$homic_rate) - .00001,
                                    philly_crimes_sf$homic_rate),
                            n = 7, 
                            style = "quantile")
breaks_qt
# breaks_qt$brks #show lower boindary of each interval
```

page 49

```{r}
philly_crimes_sf <- mutate(philly_crimes_sf, 
                           homic_rate_cat = cut(homic_rate, breaks_qt$brks)) 

ggplot(philly_crimes_sf) + 
  geom_sf(aes(fill=homic_rate_cat)) +
  scale_fill_brewer(palette = "OrRd") 
```

## section 3.4

page 49

```{r}
library(ggmap)
# tmaptools::geocode_OSM("Philadelphia")
# Philadelphia Lon is -75.16522 and Lat 39.95258 
# -75.28030  39.86700 -74.95583  40.13796 

ph_basemap <- get_stamenmap(bbox  = c(left = -75.28030, bottom = 39.86700, 
                                      right = -74.95583, top = 40.13796), 
                            zoom = 11, 
                            maptype = 'terrain-background', 
                            source = 'stamen')

ggmap(ph_basemap)
```

page 50

```{r}
ggmap(ph_basemap) +
  geom_sf(data = philly_crimes_sf, 
          aes(fill=homic_rate_cat), 
          inherit.aes = FALSE) +
    scale_fill_brewer(palette = "OrRd")
```

page 51

```{r}
# philly_crimes_sf's CRS is different with tile's CRS
# but it still can plot!
st_crs(philly_crimes_sf)
# philly_crimes_sf %>% plot()
```

```{r}
ggmap(ph_basemap) +
  geom_sf(data = philly_crimes_sf, 
          aes(fill = homic_rate_cat), 
          inherit.aes = FALSE) +
  scale_fill_brewer(palette = "OrRd") +
  coord_sf(crs = st_crs(4326))
```

## section 3.5

page 52

```{r}
library(tmap)
tmap_mode(mode = "plot")
# tmap_mode(mode = "view")
tm_shape(philly_crimes_sf) + 
  tm_polygons(col = "homic_rate", 
              style = "quantile", 
              title = "Philadelphia \nhomicide density \nper sqKm")
```

```{r}
tmap_mode("view")
tmap_last()
```

## section 3.6

page 53

```{r}
library(leaflet) 

# reproject
philly_WGS84 <- st_transform(philly_crimes_sf, crs = 4326)

leaflet(philly_WGS84) %>%
  addPolygons()
```

```{r}
pal_fun <- colorQuantile(palette = "YlOrRd", domain = NULL, n = 5)

p_popup <- paste0("<strong>Homicide Density: </strong>", philly_WGS84$homic_rate)

leaflet(philly_WGS84) %>%
  addPolygons(
    stroke = FALSE, # remove polygon borders
    fillColor = ~pal_fun(homic_rate), # set fill color with function from above and value
    fillOpacity = 0.8, smoothFactor = 0.5, # make it nicer
    popup = p_popup)  # add popup
```

```{r}
leaflet(philly_WGS84) %>%
  addPolygons(
    stroke = FALSE, 
    fillColor = ~pal_fun(homic_rate),
    fillOpacity = 0.8, smoothFactor = 0.5,
    popup = p_popup) %>%
  addTiles()
```

```{r}
leaflet(philly_WGS84) %>%
  addPolygons(
    stroke = FALSE, 
    fillColor = ~pal_fun(homic_rate),
    fillOpacity = 0.8, smoothFactor = 0.5,
    popup = p_popup) %>%
  addTiles() %>%
  addLegend(position = "bottomright",  # location
            pal = pal_fun,    # palette function
            values = ~homic_rate,  # value to be passed to palette function
            opacity = 0.7,
            title = 'Philadelphia homicide density per sqkm') # legend title
```

```{r}
# we get seven intrevals from section 3.3
philly_WGS84$homic_rate_cat %>% unique() %>% str
```

```{r}
pal_fun <- colorQuantile(palette = "YlOrRd", domain = NULL, n = 7)

leaflet(philly_WGS84) %>%
  addPolygons(
    stroke = FALSE, 
    fillColor = ~pal_fun(homic_rate),
    fillOpacity = 0.8, smoothFactor = 0.5,
    popup = p_popup) %>%
  addTiles() %>%
  addLegend("bottomright", opacity = 0.7,
            colors = brewer.pal(7, "YlOrRd"), 
            labels = paste0("up to ", format(x = breaks_qt$brks[-1], digits = 2)),
            title =  'Philadelphia homicide density per sqkm')
```

```{r}
pal_fun <- colorQuantile(palette = "YlOrRd", domain = NULL, n = 7)

leaflet(philly_WGS84) %>%
  addPolygons(
    stroke = FALSE, 
    fillColor = ~pal_fun(homic_rate),
    fillOpacity = 0.8, smoothFactor = 0.5,
    popup = p_popup,
    group = "philly") %>%
  addTiles(group = "OSM") %>%
  addProviderTiles("CartoDB.DarkMatter", group = "Carto") %>%
  addLegend("bottomright", 
            colors = brewer.pal(7, "YlOrRd"), 
            labels = paste0("up to ", format(breaks_qt$brks[-1], digits = 2)),
            title = 'Philadelphia homicide density per sqkm') %>%
  addLayersControl(baseGroups = c("OSM", "Carto"), 
                   overlayGroups = c("philly"))  
```

---

# END
